---
title: ': A Wealth of Data'
output: pdf_document
Author: 
---
```{r}
library(tidyverse)
library(stringr)
library(lubridate)
library(MASS)
library(corrplot)
library(patchwork)
library(rpart)
library(caret)
library(randomForest)
```




```{r}
library(readr)

setwd('~/Desktop/Problem_C_Data')

hair_dryer <- read_tsv(file="hair_dryer.tsv")
microwave <- read_tsv(file="microwave.tsv")
pacifier <- read_tsv(file="pacifier.tsv")
```
Cleaning

```{r}
cleaned_hair_dryer= hair_dryer %>% filter(str_detect(tolower(product_title), "dryer"))
cleaned_microwave= microwave %>% filter(str_detect(tolower(product_title), "microwave"))
cleaned_pacifier= pacifier %>% filter(str_detect(tolower(product_title), "pacifier"))
```

```{r}
write.csv(cleaned_hair_dryer,"cleaned_hair_dryer.csv")
write.csv(cleaned_microwave,"cleaned_microwave.csv")
write.csv(cleaned_pacifier,"cleaned_pacifier.csv")
```

product rating by time
```{r}
some = mdy(microwave$review_date)
as_tibble(year(some), month(some), day(some))
cleaned_microwave= cleaned_microwave %>% mutate(year= lubridate::year(mdy(review_date)),
                     month= lubridate::month(mdy(review_date)),
                     day=lubridate::day(mdy(review_date)))

cleaned_hair_dryer= cleaned_hair_dryer %>% mutate(year= lubridate::year(mdy(review_date)),
                     month= lubridate::month(mdy(review_date)),
                     day=lubridate::day(mdy(review_date)))

cleaned_pacifier= cleaned_pacifier %>% mutate(year= lubridate::year(mdy(review_date)),
                     month= lubridate::month(mdy(review_date)),
                     day=lubridate::day(mdy(review_date)))

```


```{r}

cleaned_microwave %>% filter(product_parent==423421857)%>% filter(year==2015) %>% filter(month==7)%>%  ggplot() +geom_point(mapping=aes(x=review_date,y= star_rating))


geom_smooth(data=subset(copyKVClimate, year ==1950))+geom_smooth(data=subset(copyKVClimate, year == 2019))



  cleaned_microwave %>% filter(product_parent==423421857)%>% filter(year==2015)   %>% ggplot()+ geom_histogram(mapping=aes(x=star_rating, fill=as.factor(monnth)),position="dodge",binwidth=0.7) + scale_fill_manual(breaks=1:12, values=c())
  
  
  
product1= cleaned_microwave %>% filter(product_parent==423421857)
ggplot(data=product1, mapping=aes(x=as.factor(month),group=star_rating,  color=as.factor(star_rating))) + geom_line(stat="count")+geom_point(stat="count")+facet_wrap(product1$year)


```
```{r}
cleaned_microwave %>% filter(year>=2014 ) %>%
ggplot(mapping=aes(x=as.factor(month),group=star_rating,  color=as.factor(star_rating))) + geom_line(stat="count")+geom_point(stat="count") +facet_wrap(~year)


regression_data=cleaned_microwave %>% filter(year>=2014 ) %>% group_by(review_date) %>% summarize(number=n())
regression_data


a=cleaned_microwave %>% filter(year==2014) %>% group_by(star_rating) %>% summarize(n())
a
new_some=hair_dryer_scores %>% group_by(product_id,product_parent) %>% summarize(n())
new_some
aa=new_some %>% group_by(product_parent) %>% summarize(sum(n()))
aa

```

y1=lm(y=regression_data$star_rating[regression_data$star_rating==1]~))

```
 %>% ggplot(mapping=aes(x=month, y= count ), color=as.factor(star_rating))+ geom_line()
 
 
 ggplot(copyKVClimate,aes( month, TMIN, color=as.factor(year)))+geom_smooth(data=subset(copyKVClimate, year ==1950))+geom_smooth(data=subset(copyKVClimate, year == 2019))+ggtitle("Minimum Temperatures by Month")+ylab("Minimum Temperature")+xlab("Month")

```{r}
clean_hair_dryer_scores <- read_csv("clean_hair_dryer_scores.csv")
clean_microwave_scores <- read_csv("clean_microwave_scores.csv")
clean_pacifier_scores <- read_csv("clean_pacifier_scores.csv")
hair_dryer_scores=merge(cleaned_hair_dryer,clean_hair_dryer_scores,by="review_id")
microwave_scores=merge(cleaned_microwave,clean_microwave_scores,by="review_id")
pacifier_scores=merge(cleaned_pacifier,clean_pacifier_scores,by="review_id")



unclean_hair_dryer <- read_csv("unclean_hair_dryer.csv", 
    col_types = cols(X1 = col_skip()))

unclean_microwave <- read_csv("unclean_microwave.csv", 
    col_types = cols(X1 = col_skip()))
unclean_pacifier <- read_csv("unclean_pacifier.csv", 
    col_types = cols(X1 = col_skip()))


hair_dryer_scores=merge(hair_dryer_scores,unclean_hair_dryer,by="review_id")
microwave_scores=merge(microwave_scores,unclean_microwave,by="review_id")
pacifier_scores=merge(pacifier_scores,unclean_pacifier,by="review_id")



```


```{r}
star_compous_cor=cor(hair_dryer_scores$star_rating.x,hair_dryer_scores$compound)
cor(hair_dryer_scores$star_rating.x[hair_dryer_scores$star_rating.x>3],hair_dryer_scores$compound[hair_dryer_scores$star_rating.x>3] )
star_compous_cor
cor(hair_dryer_scores$star_rating.x[hair_dryer_scores$star_rating.x<3],hair_dryer_scores$compound[hair_dryer_scores$star_rating.x<3] )
cor(hair_dryer_scores$star_rating.x[hair_dryer_scores$star_rating.x==3],hair_dryer_scores$compound[hair_dryer_scores$star_rating.x==3] )
```

boxplot
```{r}
ggplot(data=hair_dryer_scores) +geom_boxplot(mapping=aes(x=star_rating.x, y=compound,group=star_rating.x))+ggtitle("hair dryer")+
ggplot(data=microwave_scores) +geom_boxplot(mapping=aes(x=star_rating.x, y=compound,group=star_rating.x))+ggtitle("microwave")+
ggplot(data=pacifier_scores) +geom_boxplot(mapping=aes(x=star_rating.x, y=compound,group=star_rating.x))+ggtitle("pacifier")
```


```{r}
ggplot(data=hair_dryer_scores) +geom_boxplot(mapping=aes(x=star_rating.x, y=compound_unclean,group=star_rating.x))+ggtitle("hair dryer")+
ggplot(data=microwave_scores) +geom_boxplot(mapping=aes(x=star_rating.x, y=compound_unclean,group=star_rating.x))+ggtitle("microwave")+
ggplot(data=pacifier_scores) +geom_boxplot(mapping=aes(x=star_rating.x, y=compound_unclean,group=star_rating.x))+ggtitle("pacifier")
```


```{r}
par(mfrow=c(1,2))
boxplot(hair_dryer_scores$star_rating)
boxplot(hair_dryer_scores$compound)
summary(hair_dryer_scores$compound)
```
Data cleaning 
```{r}
hair_dryer_scores = hair_dryer_scores %>% dplyr::select(-star_rating.x,-X1) %>% dplyr::rename(star_rating =star_rating.y)

microwave_scores = microwave_scores %>% dplyr::select(-star_rating.x,-X1) %>% dplyr::rename(star_rating =star_rating.y)

pacifier_scores = pacifier_scores %>% dplyr::select(-star_rating.x,-X1) %>% dplyr::rename(star_rating =star_rating.y)
```


```{r}
names(hair_dryer_scores)
```
compound
compound > 0.5 == positive 
-0.5< compound < 0.5 == neutural
compound < -0.5 == negative
```{r}


hair_dryer_scores$nps=cut(hair_dryer_scores$compound, breaks=c(-1,-0.05,0.05,1), labels = c("negative","neutral","positive"))

microwave_scores$nps=cut(microwave_scores$compound, breaks=c(-1,-0.05,0.05,1), labels = c("negative","neutral","positive"))


pacifier_scores$nps=cut(pacifier_scores$compound, breaks=c(-1,-0.05,0.05,1), labels = c("negative","neutral","positive"))



hair_dryer_scores$unclean_nps=cut(hair_dryer_scores$compound_unclean, breaks=c(-1,-0.2,0.05,1), labels = c("negative","neutral","positive"))

microwave_scores$unclean_nps=cut(microwave_scores$compound_unclean, breaks=c(-1,-0.2,0.05,1), labels = c("negative","neutral","positive"))


pacifier_scores$unclean_nps=cut(pacifier_scores$compound_unclean, breaks=c(-1,-0.2,0.05,1), labels = c("negative","neutral","positive"))




```


```{r}
#table(hair_dryer_scores$star_rating, hair_dryer_scores$nps)
par(mfrow=c(1,3))
table(hair_dryer_scores$star_rating, hair_dryer_scores$unclean_nps)
table(microwave_scores$star_rating, microwave_scores$unclean_nps)
table(pacifier_scores$star_rating, pacifier_scores$unclean_nps)


par(mfrow=c(1,3))
hair_table=table(hair_dryer_scores$star_rating, hair_dryer_scores$nps)
microwave_table=table(microwave_scores$star_rating, microwave_scores$nps)
pacifier_table=table(pacifier_scores$star_rating, pacifier_scores$nps)

hair_table
microwave_table
pacifier_table
```
Chi squared test (to check if rows and columns are dependent or not)
```{r}
chisq.test(hair_table)
chisq.test(microwave_table)
chisq.test(pacifier_table)
```
There is a relationship between review and star rating 



```{r}
some_y_microwave=microwave_scores %>% filter(verified_purchase== "Y") %>% group_by(star_rating) %>% summarize(sum(helpful_votes), sum(total_votes), sum(star_rating),sum(helpful_votes)/sum(total_votes)) 
some_n_microwave=microwave_scores %>% filter(verified_purchase=="N") %>% group_by(star_rating) %>% summarize(sum(helpful_votes), sum(total_votes), sum(star_rating),sum(helpful_votes)/sum(total_votes)) 

some_y_pacifier=pacifier_scores %>% filter(verified_purchase=="Y") %>% group_by(star_rating) %>% summarize(sum(helpful_votes), sum(total_votes), sum(star_rating),sum(helpful_votes)/sum(total_votes)) 
some_n_pacifier=pacifier_scores %>% filter(verified_purchase=="N") %>% group_by(star_rating) %>% summarize(sum(helpful_votes), sum(total_votes), sum(star_rating),sum(helpful_votes)/sum(total_votes)) 
```


```{r}
some_y_hair=hair_dryer_scores %>% filter(verified_purchase== "Y") %>% group_by(star_rating) %>% summarize(sum(helpful_votes), sum(total_votes), sum(star_rating),sum(helpful_votes)/sum(total_votes)) 

some_y_hair

```
```{r}

some_n_hair=hair_dryer_scores %>% filter(verified_purchase=="N") %>% group_by(star_rating) %>% summarize(sum(helpful_votes), sum(total_votes), sum(star_rating),sum(helpful_votes)/sum(total_votes)) 
some_n_hair
```

```{r}
total_hair=hair_dryer_scores %>% group_by(star_rating) %>% summarize(sum(helpful_votes), sum(total_votes), sum(star_rating),sum(helpful_votes)/sum(total_votes)) 
total_hair
```
hair
```{r}
helpful_verified_hair=cbind(some_y_hair$`sum(helpful_votes)`,some_n_hair$`sum(helpful_votes)`)
colnames(helpful_verified_hair)<-c("Y","N")
rownames(helpful_verified_hair)=c("1","2","3","4","5")
helpful_verified_hair
helpful_verified_hair

prop.test(x=helpful_verified_hair[1,], n=c(sum(helpful_verified_hair[1,]),sum(helpful_verified_hair[1,])))
prop.test(x=helpful_verified_hair[2,], n=c(sum(helpful_verified_hair[2,]),sum(helpful_verified_hair[2,])))
prop.test(x=helpful_verified_hair[3,], n=c(sum(helpful_verified_hair[3,]),sum(helpful_verified_hair[3,])))
prop.test(x=helpful_verified_hair[4,], n=c(sum(helpful_verified_hair[4,]),sum(helpful_verified_hair[4,])))
prop.test(x=helpful_verified_hair[5,], n=c(sum(helpful_verified_hair[5,]),sum(helpful_verified_hair[5,])))
```
there is difference between Y and N's proprtion in star_rate 2,3,4,5  
there is no difference between Y and N's proprtion in star_rate 1 

```{r}
helpful_verified_hair=cbind(some_y_hair$`sum(helpful_votes)`,some_n_hair$`sum(helpful_votes)`)
colnames(helpful_verified_hair)<-c("Y","N")
rownames(helpful_verified_hair)=c("1","2","3","4","5")
helpful_verified_hair
helpful_verified_hair

prop.test(x=helpful_verified_hair[1,], n=c(sum(helpful_verified_hair[1,]),sum(helpful_verified_hair[1,])))
prop.test(x=helpful_verified_hair[2,], n=c(sum(helpful_verified_hair[2,]),sum(helpful_verified_hair[2,])))
prop.test(x=helpful_verified_hair[3,], n=c(sum(helpful_verified_hair[3,]),sum(helpful_verified_hair[3,])))
prop.test(x=helpful_verified_hair[4,], n=c(sum(helpful_verified_hair[4,]),sum(helpful_verified_hair[4,])))
prop.test(x=helpful_verified_hair[5,], n=c(sum(helpful_verified_hair[5,]),sum(helpful_verified_hair[5,])))
```


```{r}
helpful_verified_microwave=cbind(some_y_microwave$`sum(helpful_votes)`,some_n_microwave$`sum(helpful_votes)`)
colnames(helpful_verified_microwave)<-c("Y","N")
rownames(helpful_verified_microwave)=c("1","2","3","4","5")
helpful_verified_microwave
helpful_verified_microwave

prop.test(x=helpful_verified_microwave[1,], n=c(sum(helpful_verified_microwave[1,]),sum(helpful_verified_microwave[1,])))
prop.test(x=helpful_verified_microwave[2,], n=c(sum(helpful_verified_microwave[2,]),sum(helpful_verified_microwave[2,])))
prop.test(x=helpful_verified_microwave[3,], n=c(sum(helpful_verified_microwave[3,]),sum(helpful_verified_microwave[3,])))
prop.test(x=helpful_verified_microwave[4,], n=c(sum(helpful_verified_microwave[4,]),sum(helpful_verified_microwave[4,])))
prop.test(x=helpful_verified_microwave[5,], n=c(sum(helpful_verified_microwave[5,]),sum(helpful_verified_microwave[5,])))
```
```{r}
helpful_verified_pacifier=cbind(some_y_pacifier$`sum(helpful_votes)`,some_n_pacifier$`sum(helpful_votes)`)
colnames(helpful_verified_pacifier)<-c("Y","N")
rownames(helpful_verified_pacifier)=c("1","2","3","4","5")
helpful_verified_pacifier
helpful_verified_pacifier

prop.test(x=helpful_verified_pacifier[1,], n=c(sum(helpful_verified_pacifier[1,]),sum(helpful_verified_pacifier[1,])))
prop.test(x=helpful_verified_pacifier[2,], n=c(sum(helpful_verified_pacifier[2,]),sum(helpful_verified_pacifier[2,])))
prop.test(x=helpful_verified_pacifier[3,], n=c(sum(helpful_verified_pacifier[3,]),sum(helpful_verified_pacifier[3,])))
prop.test(x=helpful_verified_pacifier[4,], n=c(sum(helpful_verified_pacifier[4,]),sum(helpful_verified_pacifier[4,])))
prop.test(x=helpful_verified_pacifier[5,], n=c(sum(helpful_verified_pacifier[5,]),sum(helpful_verified_pacifier[5,])))
```



```{r}
helpful_verified
```

```{r}
a=hair_dryer_scores %>% group_by(product_id) %>% summarize(n())
new_some=hair_dryer_scores %>% group_by(product_id,product_parent) %>% summarize(n())
new_some
aa=new_some %>% group_by(product_parent) %>% summarize(sum(n()))
aa
length(new_some$product_parent)
length(unique(new_some$product_parent))
```

```{r}
p1=hair_dryer_scores %>% group_by(product_parent) %>% summarize(number=n()) %>% filter(number>200)
hair_dryer_scores %>% filter( product_parent %in% p1$product_parent) %>% filter(year>2010) %>% 
ggplot(mapping=aes(x=as.factor(year),group=1)) +geom_point(stat="count")+geom_line(stat="count") +facet_wrap(~product_parent)

p2=microwave_scores %>% group_by(product_parent) %>% summarize(number=n()) %>% filter(number>70)
microwave_scores %>% filter( product_parent %in% p2$product_parent) %>% filter(year>2010) %>% 
ggplot(mapping=aes(x=as.factor(year),group=1)) +geom_point(stat="count")+geom_line(stat="count") +facet_wrap(~product_parent)

smicrowave_scores %>% group_by(product_parent) %>% summarize(number=n())

p3=pacifier_scores %>% group_by(product_parent) %>% summarize(number=n()) %>% filter(number>200)
pacifier_scores %>% filter( product_parent %in% p3$product_parent) %>% filter(year>2010) %>% 
ggplot(mapping=aes(x=as.factor(year),group=1)) +geom_point(stat="count")+geom_line(stat="count") +facet_wrap(~product_parent)
```


```{r}
adjectives_microwave <- read_csv("adjectives_microwave.csv")
adjectives_hair_dryer <- read_csv("adjectives_hair_dryer.csv", 
    col_types = cols(X1 = col_skip()))
adjectives_pacifier <- read_csv("adjectives_pacifier.csv", 
    col_types = cols(X1 = col_skip()))
```

```{r}
View(adjectives_microwave %>% filter(count>100))
View(adjectives_microwave %>% filter(count<100))

View(adjectives_hair_dryer %>% filter(count>100))
View(adjectives_hair_dryer %>% filter(count<100))

View(adjectives_pacifier %>% filter(count>100))
View(adjectives_pacifier %>% filter(count<100))
```

```{r}
hair_dryer_words <- read_csv("hair_dryer_words.csv", 
    col_types = cols(X1 = col_skip()))

microwave_words <- read_csv("microwave_words.csv", 
    col_types = cols(X1 = col_skip()))

pacifier_words <- read_csv("pacifier_words.csv", 
    col_types = cols(X1 = col_skip()))

```


```{r}
hair_dryer_scores_words=merge(hair_dryer_scores,hair_dryer_words,by="review_id")
microwave_scores_words=merge(microwave_scores,microwave_words,by="review_id")
pacifier_scores_words=merge(pacifier_scores,pacifier_words,by="review_id")
View(hair_dryer_scores_words)


table(hair_dryer_scores_words$star_rating,hair_dryer_scores_words$perfect)
table(hair_dryer_scores_words$star_rating,hair_dryer_scores_words$great)
```


```{r}
hair_dryer_scores_words$perfect[hair_dryer_scores_words$perfect==T]
```
```{r}
rfx=hair_dryer_scores_words %>% dplyr::select(perfect,great, awesome, super, powerful, bad, noisy, hard, disappointed, difficult)
rf.x.numeric=as.factor(rfx$perfect)
rf.y=hair_dryer_scores_words %>% dplyr::select(star_rating)
rf.y
aaa=data.frame(as.integer(rf.x))
bbb=data.frame(as.factor(rf.y))
fit.rf=randomForest(x=aaa, y=rf.y)
text(model, digits = 3)
```

